---
title: "caretStack Summary"
output:
  html_document:
    theme: yeti
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(caretStack)
library(RColorBrewer)
library(scales)
library(ROCR)

# Remember to set these variables before running. You do not need to make any other changes to run the summary template.
data <- read.csv('_____.csv', stringsAsFactors = F)
predictor_var_file_list <- "_____.csv"
outDir <- '_____'
var_to_predict <- "_____"
rNCVdir <- "_____"
rdata_prefix <-"_____"
targetType <- "_____"
nRep <- _____
nFolds.outer <- _____
```

## Target: `r var_to_predict`

### Predictors: `r predictor_var_file_list`

```{r}
filename <- paste0(outDir, "/", var_to_predict, "_",rdata_prefix, '.results.RData')

load(filename)

if(targetType %in% c("binary", "categorical")){
  this_plot_data <- table(data[,var_to_predict])
  my_bar <- barplot(this_plot_data, 
                    ylim = c(0, max(this_plot_data)*1.25), 
                    col = brewer.pal(n = 10, name = "Spectral")[runif(1, 1, 10)])
  text(my_bar, 
       this_plot_data +  max(this_plot_data)*.05, 
       this_plot_data)
}else{
  hist(data[,var_to_predict], 
       xlab = var_to_predict, 
       main = paste0("Histogram of ", var_to_predict),
       col = brewer.pal(n = 10, name = "Spectral")[runif(1, 1, 10)])
}
```

```{r}
summ <- read.csv(paste0(outDir, "/", var_to_predict, "_", rdata_prefix,'_summary.csv'))

unique(summ$metric)

if("Sensitivity" %in% unique(summ$metric)){
  metrics <- c("Sensitivity", "Specificity",  "AUC")
}else if("Mean_Sensitivity" %in% unique(summ$metric)){
  metrics <- c("Mean_Sensitivity", "Mean_Specificity",  "AUC")
}else if("RMSE" %in% unique(summ$metric)){
  metrics <- c("MAE","RMSE","Rsquared")}

summary_plot(summ, "Summary", metrics = metrics)
```

```{r}
filename <- paste0(outDir, "/", var_to_predict, "_", rdata_prefix, '_VarImp.csv')

combined_vals <- read.csv(filename)

ntest <- nrow(combined_vals)
# Number of rejected hypotheses

if(targetType == "binary"){
  
  plot.dset <- data.frame(variable = combined_vals$variable,
                          cmpvar = combined_vals$cohens_d,
                          pval = combined_vals$t_test_pval,
                          col = combined_vals$greater.mean,
                          ML_Varimp = combined_vals$ML_Varimp)
  my.xlab <- "Cohens D"
}else if(targetType == "numerical"){
  combined_vals$col <- ifelse(combined_vals$r > 0, "positive", "negative")
  my.xlab <- "R"
  plot.dset <- data.frame(variable = combined_vals$variable,
                          cmpvar = combined_vals$r,
                          pval = combined_vals$pval,
                          col = combined_vals$col,
                          ML_Varimp = combined_vals$ML_Varimp)
}else if(targetType == "categorical"){
  plot.dset <- data.frame(variable = combined_vals$variable,
                          cmpvar = NA,
                          pval = NA,
                          col = NA,
                          ML_Varimp = combined_vals$ML_Varimp)
}
```

```{r}
cor_val <- cor(plot.dset$cmpvar , plot.dset$ML_Varimp)

if(!targetType == "categorical"){
plot(plot.dset$cmpvar^2, plot.dset$ML_Varimp, xlab = paste0(my.xlab, "^2"), ylab = 'ML Variable Importance',
     main = paste('r =', round(cor_val, digits = 2)))
}
```

```{r,fig.width=10, fig.height=25}
fdr.adj <- p.adjust(plot.dset$pval, method = "fdr")
bon.adj <- p.adjust(plot.dset$pval, method = "bonferroni")

bon.thr <- 0.05/length(plot.dset$pval)
fdr.thr <- sort(plot.dset$pval)[sum(fdr.adj<0.05)]


par(mar = c(5, 4, 4, 4) + 0.1)

my.gplot <- ggplot(plot.dset, 
                   aes(x = variable, y = -log(pval), color = col)) +   
  geom_segment(aes(x = variable , y = 0, xend = variable, yend = -log(pval)), size = 0.25) +
  geom_hline(yintercept = -log(bon.thr)) + 
  geom_hline(yintercept = -log(fdr.thr)) + 
  geom_hline(yintercept = -log(0.05)) + 
  annotate("label", x = nrow(plot.dset)*.75, y = -log(bon.thr), label = "Bonf 0.05") +
  annotate("label", x = nrow(plot.dset)*.75, y = -log(fdr.thr), label = "FDR 0.05") +
  annotate("label", x = nrow(plot.dset)*.75, y = -log(0.05), label = "P-val 0.05") +
  geom_point() +
  xlab("variable") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  coord_flip()

if(!targetType == "categorical"){
plot(my.gplot)
}
```

#### Variables with Bonferonni corrected p-value < 0.05: `r sum(plot.dset$pval <= bon.thr)`

#### `r if(length(fdr.thr)>0){paste0("Variables with FDR corrected p-value < 0.05: ", sum(plot.dset$pval <= fdr.thr))}`

#### Variables with p-value < 0.05: `r sum(plot.dset$pval <= 0.05)`

```{r}
hist(plot.dset$ML_Varimp, 
     xlab = "Variable Importance", 
     main = "Histogram of Variable Importance",
     col = brewer.pal(n = 10, name = "Spectral")[runif(1, 1, 10)])
```

```{r,fig.width=12, fig.height=50, warning=F}
  pos.group <- plot.dset$col[plot.dset$cmpvar > 0][1]
  neg.group <- plot.dset$col[plot.dset$cmpvar < 0][1]
  
if(targetType == "binary"){
  fill.name1 <- paste0("Cohens D (", pos.group,")")
  fill.name2 <- paste0("-Cohens D (", neg.group,")")
}else{
  fill.name1 <- "R"
  fill.name2 <- "-R"
}
  plot.dset$significance <- ""
  plot.dset$significance[plot.dset$pval <= 0.05] <- "*"
  plot.dset$significance[plot.dset$pval <= fdr.thr] <- "**"
  plot.dset$significance[plot.dset$pval <= bon.thr] <- "***"
  
  #plot.dset$sigvar_name <- paste0(plot.dset$significance, plot.dset$variable)
  
  max_this_VarImp <- max(plot.dset$ML_Varimp)
  n <- dim(plot.dset)[1]
  
  scale.xax <- max(plot.dset$ML_Varimp)/abs(plot.dset$cmpvar[which.max(plot.dset$ML_Varimp)])*.5
  
  gg <- ggplot(plot.dset, aes(x = reorder(variable, ML_Varimp))) +
    coord_flip() +
    geom_col(aes(y = ML_Varimp, fill = "Variable Importance"), alpha = .9)+
    geom_text(aes(y = ML_Varimp, label = round(ML_Varimp, 1)), hjust = 0)+
    
    geom_col(aes(y = cmpvar*scale.xax, fill = fill.name1), alpha = .9) +
    geom_col(aes(y = cmpvar*-1*scale.xax, fill = fill.name2), alpha = .9) +
    geom_text(aes(y = abs(cmpvar)*scale.xax, label = paste0(round(cmpvar, 2), significance)), hjust = 0)+
    
    theme(legend.position = "right",legend.justification = c(0, 1),
          axis.text.x = element_blank(),
          plot.margin = unit(c(1,1,1,1), "cm",),
          # ,aspect.ratio = n/10
          panel.background = element_blank()
    )+
    scale_fill_manual(values=c("pink","lightblue", "grey"))+
    ylim(0,max_this_VarImp + 5) # Will cause warning "Removed [x] rows containing missing values (position_stack)." This is because the negative values are hidden, and it is nothing to worry about.
  
  plot(gg)
```

#### Top 10 Variable Importance:
  `r paste(plot.dset$variable[order(plot.dset$ML_Varimp, decreasing = T)][1:10], collapse = ", ")`

#### `r if(targetType != "categorical"){paste0("Top 10 magnitude ", my.xlab, ":")}`
  `r if(targetType != "categorical"){paste(plot.dset$variable[order(abs(plot.dset$cmpvar), decreasing = T)][1:10], collapse = ", ")}`

```{r,fig.width=8, fig.height=8}
if(targetType == "binary"){
  PredVal_filename <- paste0(outDir, "/", rNCVdir, "/", rdata_prefix, "/", var_to_predict, "_", rdata_prefix, '_Rep_',1,'_fold_',1,'-PredVal.rda')
load(PredVal_filename)

my.methods <- names(pred.val$prediction$test)

for(method in my.methods){
  n_test <- nrow(pred.val$prediction$test[[method]])
  
  conf <- list()
  
  fpr <- list()
  tpr <- list()
  thr <- list()
  
  cols <- rainbow(25, alpha =0.25)
  for(i in 1:nRep){
    for(j in 1:nFolds.outer){
      PredVal_filename <- paste0(outDir, "/", rNCVdir, "/", 
                                 rdata_prefix, "/", var_to_predict, "_", 
                                 rdata_prefix, '_Rep_',i,'_fold_',j,'-PredVal.rda')
      load(PredVal_filename)
      
      
      
      ref.lv <- levels(pred.val$prediction$test[[method]]$obs)[2]
      
      preds <- pred.val$prediction$test[[method]][ref.lv]
      labs <- as.numeric(pred.val$prediction$test[[method]]$obs)
      
      
      # My own method for creating ROC curve
      srt.pred <- order(preds[,1], decreasing = T)
      preds.srt <- preds[srt.pred,1]
      labs.srt <- labs[srt.pred]
      
      thr[[j+(i-1)*nFolds.outer]] <- preds.srt
      thr.unq <- unique(preds.srt)
      fpr[[j+(i-1)*nFolds.outer]] <- sapply(1:length(thr.unq), function(x){sum(labs.srt[preds.srt >= thr.unq[x]] == 1)}) / sum(labs.srt == 1)
      tpr[[j+(i-1)*nFolds.outer]] <- sapply(1:length(thr.unq), function(x){sum(labs.srt[preds.srt >= thr.unq[x]] == 2)}) / sum(labs.srt == 2)
      
      my.title <- paste0("ROC: Predicting ",var_to_predict, " using ",method, " method.")
      
      if(i == 1 && j == 1){
        plot(fpr[[j+(i-1)*nFolds.outer]], tpr[[j+(i-1)*nFolds.outer]], main = my.title, type = 'l', col = cols[j+(i-1)*nFolds.outer], xlab = "False Positive Rate", ylab = "True Positive Rate")
      }else{
        lines(fpr[[j+(i-1)*nFolds.outer]], tpr[[j+(i-1)*nFolds.outer]], main = my.title, col = cols[j+(i-1)*nFolds.outer])
      }
      abline(a = 0,b = 1)
      
    }
  }
  
  ninterp <- length(fpr[[1]])
  fpr_interp <- seq(0,1, length.out = ninterp)
  
  tpr_interp <- lapply(1:(nFolds.outer*nRep), function(x){approx(fpr[[x]], tpr[[x]], fpr_interp, ties = min)$y})
  tpr_interp <- lapply(tpr_interp, function(x){x[is.na(x)] <- 0; return(x)})
  
  tpr_avg <- sapply(1:ninterp, function(x){mean(unlist(lapply(tpr_interp,'[', x)))})
  tpr_sd <- sapply(1:ninterp, function(x){sd(unlist(lapply(tpr_interp,'[', x)))})
  
  lines(fpr_interp, tpr_avg, col = "red")
  lines(fpr_interp, tpr_avg + tpr_sd, col = "red")
  lines(fpr_interp, tpr_avg - tpr_sd, col = "red")
}
}
```

```{r,fig.width=8, fig.height=8}
if(targetType == "binary"){
  PredVal_filename <- paste0(outDir, "/", rNCVdir, "/", rdata_prefix, "/", var_to_predict, "_", rdata_prefix, '_Rep_',1,'_fold_',1,'-PredVal.rda')
  load(PredVal_filename)
  
  my.methods <- names(pred.val$prediction$test)
  
  for(method in my.methods){
    n_test <- nrow(pred.val$prediction$test[[method]])
    
    conf <- list()
  for(i in 1:nRep){
    for(j in 1:nFolds.outer){
        PredVal_filename <- paste0(outDir, "/", rNCVdir, "/", rdata_prefix, "/", var_to_predict, "_", rdata_prefix, '_Rep_',i,'_fold_',j,'-PredVal.rda')
        load(PredVal_filename)
        
        library(ROCR)
        
        #ref.lv <- as.character(data[1, var_to_predict])
        ref.lv <- levels(pred.val$prediction$test[[method]]$obs)[2]
        preds <- pred.val$prediction$test[[method]][ref.lv]
        labs <- as.numeric(pred.val$prediction$test[[method]]$obs)
        
        
        pred <- prediction(preds, labs)
        perf <- performance(pred,"tpr", "fpr")
        
        my.title <- paste0("ROC: Predicting ",var_to_predict, " using ",method, " method.")
        
        
        if(i == 1 && j == 1){
          plot(perf, colorize = TRUE, main = my.title)
        }else{
          plot(perf, colorize = TRUE, add = T)
        }
        abline(a = 0,b = 1)
        
        preds2 <- pred.val$prediction$test[[method]]$pred
        labs2 <- pred.val$prediction$test[[method]]$obs
        conf[[j+(i-1)*nFolds.outer]] <- confusionMatrix(preds2, labs2)$table
      }
    }
    print(paste0("Confusion Matrix: Predicting ",var_to_predict, " using ",method, " method."))
    print(apply(simplify2array(conf), 1:2, mean))
  }
}
```






